TIMES Ireland Model: Residential Sector

### 2021-06-01 manuscript.tex
Break

Hedegard and Münster used....

@@

%Space Heating demand - BER space heating is only within certain months and assumes 21C heating..
\subsubsection{Space and Water Heating}
Capacity, Efficiency, Constraints, Uptake, adapation
\subsubsection{Lighting, Appliances and Other}
Capacity, Efficiency, Constraints, Uptake, adapation
\subsubsection{User Constraints}
\label{LitR:Constraints}

>>>>

Hedegard and Münster \cite{Hedegaard2013InfluenceOperation} utilised Balmorel model to analyse how heat pumps with  complementing heat storages affect wind power investments in Denmark. A westeren and eastern region is used and the model covers norway,sweden, finland and germay in order to cover import/export 
Thermal building model add-on: Theoptimisation is done subject to a number of constraints includingsatisfaction of demands for electricity and heat in each time period,renewable energy potentials, and technical restrictions on units
almorel is used for handling theintegrated power and district heating system.

nd reduce the need for peak and reservecapacity
Results show thatthe heat pumps, even without flexible operation, can contribute significantly to facilitating larger windpower investments and reducing system costs, fuel consumption, and CO2emissions
NOTE- The model is deterministic assuming perfect foresightand the linear version applied does not include start-up costs, min-imum load requirements, or part load efficiencies
Modelled indivaully heated - RESULT When invest-ments in individual heat pumps are allowed (iHP and iHP-Flex sce-nario), air–water heat pumps are installed in all individuallyheated areas. This represents a significant electricity demand
inidentifying individual heat pumps as highly socio-economicallycompetitive in non-district heating areas. Our results indicate thatin terms of making wind power investments more attractive andreducing system costs, fuel consumption, and CO2emissions, theinstallation of the heat pumps is the most important step, whilethe system benefits of adding flexibility to the heat pumps aremoderate. When investing in individual heat storages, the heat pumpscontribute in peak load shaving, and their operation is prioritisedfor hours with low electricity prices. However, the flexible opera-tion provides only moderate system benefits. Hereof, the mainbenefit is a reduced need for peak/reserve capacity investmentsof about 300–600 MW for the case analysed, corresponding tothe size of a large power plant.

@@

%Space Heating demand - BER space heating is only within certain months and assumes 21C heating..
\subsubsection{Space and Water Heating}
Capacity, Efficiency, Constraints, Uptake, adapation
heat output (Qt) and electricity input in a given time per-iod (Pt) is expressed asQt= COPPt, where COP is the average an-nual coefficient of performance for the heat pump
\subsubsection{Lighting, Appliances and Other}
Capacity, Efficiency, Constraints, Uptake, adapation
\subsubsection{User Constraints}
\label{LitR:Constraints}
